Computer-Assisted Analysis of the \\ Anderson-Hájek Ontological Controversy

### 2015-07-16 Papers/InProgress/HajekAndersonControversy/main.tex
Move definitions

\begin{definition}
An axiom $A$ is \textbf{redundant} w.r.t. a set of axioms $S$ iff $A$ is
entailed by $S$. \end{definition}

@@

\begin{definition}
An axiom $A$ is \textbf{superfluous} w.r.t. a set of axioms $S$ iff T3 is
entailed by $S \setminus \{ A \}$.
\end{definition}

@@

\begin{definition}
  An axiom $A$ is \emph{independent} of a set of axioms $S$ iff
  there are models of $S$ where $A$ is true and other models of
  $S$ where $A$ if false.
\end{definition}

>>>>

\begin{samepage}
The following definitions of redundancy, superfluousness and independence are used throughout this paper:

\begin{definition}
An axiom $A$ is \textbf{redundant} w.r.t. a set of axioms $S$ iff $S$ entails $A$. 
\end{definition}

\begin{definition}
An axiom $A$ is \textbf{superfluous} w.r.t. axiom set $S$ iff $S \setminus \{ A \}$ entails T3.
\end{definition}

\begin{definition}
  An axiom $A$ is \textbf{independent} of a set of axioms $S$ iff
  there are models of $S$ where $A$ is true and other models of
  $S$ where $A$ if false.
\end{definition}
\end{samepage}

\clearpage

@@

@@
